\section{Message from the General Chair}\vspace{2em}
\setheaders%
    {Message from the General Chair}%
    {Message from the General Chair}
\thispagestyle{emptyheader}

\setlength{\parskip}{1ex}

Welcome to NAACL HLT 2016!  This year's conference is held in San Diego,
California, where we have assembled an exciting program of computational
linguistics research.

The main program features a wide array of topics, and it includes
excellent invited talks by Prof. Regina Barzilay and Prof. Ehud Reiter.
In addition, we have six tutorials on the day before the main program,
plus fifteen workshops on the following two days. Some of these
workshops are back for their 10th or 11th incarnation, while others are
brand-new.  In parallel, we have a live demonstration track, and a
Student Research Workshop that showcases work by the junior members of
our research community.

This NAACL HLT meeting takes place only through the hard work of many
people who deserve our gratitude.

Thanks to Priscilla Rasmussen for making local arrangements, handling
registration, setting up social events, writing visa invitation letters,
and solving a myriad of issues.  Priscilla, your experience is a great
asset to any conference!

The NAACL HLT organizing committee took all the steps to bring you a
great conference.  Many thanks to Ani Nenkova and Owen Rambow (Program
Co-chairs), Mohit Bansal and Alexander M. Rush (Tutorial Co-chairs),
Radu Soricut and Adrià de Gispert (Workshop Co-chairs), Jacob Andreas,
Eunsol Choi, and Angeliki Lazaridou (Student Research Workshop
Co-Chairs) and their faculty advisors Jacob Eisenstein and Nianwen Xue,
Aliya Deri (Student Volunteer Coordinator), Julie Medero (Local
Sponsorship Chair), Mark Finlayson, Sravana Reddy, and John DeNero
(Demonstration Co-chairs), Adam Lopez and Margaret Mitchell
(Publications Co-chairs), Jason Riesa (Website Chair), Wei Xu (Publicity
Chair), and Jonathan May (Social Media Chair).

Thanks also to the NAACL Board for providing excellent advice, and
thanks to previous chairs for their suggestions and timelines.

Sponsors of NAACL HLT 2016 include Baidu and Google (Platinum Sponsors),
Amazon, Bloomberg, eBay, Microsoft Research, and UnitedHealth Group
(Gold Sponsors), Huawei (Silver Sponsors), Civis Analytics, Facebook,
@newsela, and Nuance (Bronze Sponsors), and the University of Washington
(Supporter).  Thanks for your extremely valuable contributions!

\newpage 

Finally, thanks to the scientists, engineers, authors, and attendees who
come to share and learn at this leading venue for computational
linguistics research!

\vskip 0.3in
\noindent Kevin Knight\\
Information Sciences Institute, University of Southern California\\
NAACL HLT 2016 General Chair

\index{Knight, Kevin}
